---
title: "Alcohol vs Seat choice"
author: "Giselle Gonzalez"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

The data came from UCDavis in the year ...

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods 
In the data set davisdata seat is a categorical variable, alcohol is numerical

We try to predict alcohol based on where you sit. So we use the numerical~categorical helper file

# Results

## Descriptive Results 

### Graphical summary 
```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
 Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

 This boxplot shows that there are more students sitting in the back who drink alcohol then the front and middle row  
 
## Numerical summary

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
## InferentiaL Results
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

the p value is 0.000116, is less than 0.05 so we reject the null hypothesis    

There is a difference in alcohol consumption based on where people sit  


```{r}
plot(TukeyHSD(model1))
```

This shows that the middle-back and front-back consume more alcohol then middle-front

## Conclusions
In conclusion our goal was to find out if there a difference between the alcohol consumed between the row you choose to sit in? We did find out that there is a difference between the rows using the tukey test data and we also reject the null hypothesis because it is 0.000116 is less than 0.05

